Benchmarking FDR Methods - Alternative Settings

### 2017-11-03 datasets/simulations/analysis-01-plot.Rmd
Parse t-test simulations at alpha = 0.05

```{r, load-libraries, message=FALSE}
library("dplyr")
library("ggplot2")
library("viridis")
library("data.table")
library("SummarizedBenchmark")
```

@@

>>>>

```{r, load-libraries, message=FALSE}
library("data.table")
library("SummarizedBenchmark")
library("tidyverse")
library("magrittr")
```

@@

<!-- ######################################################################## -->
## Plot Cross-Setting Metrics (100 replications) just "alpha = 0.05"
<!-- ######################################################################## -->

In the previous section, we generated a single plot for each metric under each simulation setting as a function of the nominal FDR threshold over a range of 0.01 to 0.10. In this section, we instead just focus on the FDR threshold of 0.05 and generate plots as a function of the simulation settings. Thus, each family of simulation settings is reduced to a single plot for each metric, making it easier to summarize and compare the performance of each method across a large set of settings.

Here, we simply parse and save the merged performance metrics. Results are plotted in `analysis-03-plot.Rmd`.

```{r}
library("tidyverse")
library("SummarizedBenchmark")

## list of results from 100 replication experiments
dl <- list.dirs("data-tsim/M100", recursive=FALSE, full.names=TRUE)

## running in batch
for (dd in dl) {
    fl <- list.files(dd, pattern=".rds", full.names=TRUE)

    ## generate same plots for all parameter settings
    tsbl <- list()
    for (f in fl) {
        t1 <- proc.time()
        ## read process data
        res <- readRDS(f)
        tsb <- plotsim_standardize(res, alpha = 0.05)
        tsbs <- tsb %>%
            filter(!(blabel %in% c("bl-df02", "bl-df04", "bl-df05", 
                                   paste0("ihw-a0", c(1:4, 6:9)), "ihw-a10")),
                   alpha == 0.05) %>%
            select(blabel, performanceMetric, value, rep)
        tsbl[[gsub(".*/(.*)\\.rds", "\\1", f)]] <- tsbs
        print(paste0("done with ", f, "; time: ", proc.time()[3] - t1[3]))
    }
    tsbc <- bind_rows(tsbl, .id = "param") %>% as.tibble

    ## save the parsed tables for easier future access
    saveRDS(tsbc, file.path(dd, "results-performanceMetrics-alpha05.rds"))
}
```
